Compact Core Galaxies in the RESOLVE Survey

### 2016-05-11 paperdraft.tex
paper draft 3

CSSs have half-light radii (\Reff) ranging typically from $\sim$10--600 pc \citep[e.g.,][]{Norris2014}, and there are multiple ideas for how they form. The smaller of the CSSs, UCDs may simply be the high mass extension of the GC population \citep{Drinkwater2000, Mieske2002}. The is also evidence that UCDs are created via the tidal stripping of nucleated dwarf galaxies \citep{Bekki2001, Bekki2003, Jennings2015, Zhang2015}. \citet{Seth2014} find a supermassive black hole at the center of another UCD, providing further evidence of tidal stripping being common for UCDs. Similarly, cEs are thought to be the result of tidal stripping events, as argued for the prototypical cE, M32 \citep{Choi2002, Graham2002, Huxor2011}. More evidence is provided by the discovery of tidal streams near cEs \citep{SmithCastelli2008a,Chilingarian2009} and one cE, studied in \citet{Kormendy1997}, that is believed to host a central massive black hole. On the other hand, \citet{Wirth1984}, \citet{Kormendy2009}, and \citet{Kormendy2012a} argue that cEs are the low mass extension to the normal E population created via dissipative formation in gas rich environments, such as mergers or in the two-phase formation process detailed in \citet{Oser2010}. One of the most successful recent searches for CSSs is the AIMSS catalog \citep{Norris2014}: with many newly discovered UCDs and cEs to examine, the authors argue that all of the above scenarios for UCD and cE formation occur.

In contrast to CSSs, dwarf elliptical galaxies \citep[dEs;][]{Sandage1985} and their nucleated counterparts \citep[dE,Ns;][]{Binggeli1984} are quite common, especially in clusters where they were first discovered. In fact, \citet{Binggeli1991} find that of 225 galaxies present in the center of Virgo cluster, 174 are classified as dEs or dE,Ns based on their surface brightness profiles. While dEs are typically larger than CSSs with half light radii ranging from $\sim600$~pc up to $\sim2000$~pc \citep[e.g.,][]{Norris2014}, the cores of dE,Ns can reach down to CSS-like sizes and reside within larger envelopes that are dE-sized. Similar to cEs, dEs are often thought to be either tidally stripped remnants \citep{Crnojevi2014} or the low mass extension to elliptical galaxies \citep{Kormendy2012a}. They could also be the remnants of late-type disk galaxies or luminous blue compact dwarfs that have been ram-pressure stripped and quenched as they enter the cluster environment \citep{Lisker2013, Crawford2016a}. There is also some evidence that dE,Ns are progenitors of UCDs as they fall deeper into the cluster core and are further stripped \citep{Pfeffer2013,Zhang2015,Liu2015}.

Given the similarities in formation scenarios between CSSs and dEs, we introduce the term ``compact core galaxy'' or ``CCG'' to encompass CSSs and dEs with core radii up to 800~pc. The goal of this paper is to study these galaxies as part of a continuum of compact galaxies in order to differentiate between formation scenarios. Clues to how CCGs form may be given by their environments,  morphology i.e., one- or two-component structure, star formation histories, and kinematics. We highlight these data below.

%environments
\textit{Environments.} CSSs have been found in a large range of environments thus far. UCDs were first discovered in the Fornax cluster \citep{Hilker1999, Drinkwater2000} and have since been found in the cores of several other clusters \citep{Price2009,Madrid2010,Jones2006,Mieske2009,Misgeld2008}, in groups \citep{Evstigneeva2007}, and near field galaxies \citep{Hau2009,Norris2011}. M32 was first discovered in our Local Group \citep{Faber1973} near M31, and more cEs have later been found in clusters \citep{Chilingarian2007,SmithCastelli2012,Price2009} and other groups \citep{Huxor2011,Chilingarian2010}. As stated previously, dEs and dE,Ns are common in clusters \citep{SmithCastelli2012,Koo1994,Guzman1996,Crawford2016a}, but have also been found near groups \citep{Crnojevi2014,Penny2014}. Only cEs have been found ``free floating'', meaning there is no host galaxy at all: \citet{Huxor2013} and \citet{Paudel2014} find cEs separated from other galaxies by $>1$~Mpc.

@@

%structure
\textit{Morphologies.} CSSs have been found to exhibit either one component (i.e., just a core) or two component (i.e., a core plus a surrounding envelope of gas and stars) morphology. \citet{Graham2002} have shown that M32's light profile is best fit with a core plus a surrounding exponential disk profile, which they argue points toward a tidal-stripping origin. \citet{Pfeffer2013} use N-body simulations to predict that UCDs that are tidally stripped remnants will also display multi-component surface brightness profiles due to lingering outer galaxy structures. Conversely, dissipative processes such as the two-phase formation scenario proposed by \citet{Oser2010} cause cores to form as gas rushes to the center and star formation begins. This core is then ``puffed up'' through time as it interacts with other galaxies. The free-floating cE discovered in \citet{Huxor2013}, shown to have only a one-component light profile, may be an example of the first step in this two-phase formation. It's important to note that these effects may vary based on the degree of stripping and how much time has passed since the stripping or dissipative formation occurred.

@@

For dEs and dE,Ns, there is similar diversity in colors. \citet{Drinkwater2000} and \citet{Ferrarese2006} find that the cores of dE,Ns tend to have younger stellar populations compared to their host galaxies. \cite{Grant2005} also find that two-fifths of the Virgo dE,Ns have young cores compared to their envelopes, while three-fifths display the opposite trend.

@@

  We use the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog \citep{Norris2014,Forbes2014,Janz2015} as a reference sample for our CCGs.  AIMSS is a catalog of spectroscopically confirmed CSSs found near field galaxies and in groups and clusters, and includes both previously known and newly discovered objects. The AIMSS CSS discovery process was as follows. First, a search was conducted in the HyperLeda redshift catalog \citep{Paturel2003} for all galaxies with M$_{\rm B}~<~-15$ and distances between $\sim 7$ and 200 Mpc (close enough to ensure any CSSs with \Reff\ $> 50$ pc would be resolved in any available HST imaging). The team then searched the Hubble Space Telescope archive for WFCP2, ACS, and WFC3 imaging within 150 kpc in projection of the selected galaxies. Next, Source Extractor was run on the HST images, and candidates were identified using a training set of previously known CSSs from the literature. After vetting by eye and cross-matching to ensure none are previously known, spectra were obtained for redshift confirmation and measurements of velocity dispersions. AIMSS also includes literature data for previously known UCDs, cEs, (nucleated) dEs, dwarf spheroidals, dwarf S0s, young massive clusters, and Es. The catalog provides a compilation of absolute $V$-band magnitude, stellar mass, half-light radius, and velocity dispersion for each of its objects. Thus, though not a statistically-defined sample, AIMSS provides a useful reference catalog to which we can compare our CCGs. We also note that the objects in AIMSS are not decomposed, meaning their \Reff\ are all single component fits. We discuss this more in \autoref{discussion}.

@@

\textsc{Galfit} needs the following input files to function correctly: an initial input file, an image of the galaxy, a PSF image, an image mask, and a constraint file. We obtain or construct these items as follows:

@@

\item[The initial input file]{The initial input file gives \textsc{Galfit} the file paths to the image, PSF, mask, and constraint file, and also holds the initial guesses for our fit parameters. For the one component fits, we set up our input file to include a section to measure the level of the sky background and another section to fit a S\'ersic profile to the galaxy. The S\'ersic model will find a best fit for the following parameters: central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle. These initial values for these parameters can just be rough guesses, but for our purposes, we use values for the magnitude, \Reff, b/a, and PA that are derived from RESOLVE's custom processed photometric data (see \autoref{phot} for more details).}

@@

where $\Sigma_e$ is the surface brightness at \Reff, $R(C_0; m)$ is a geometric correction factor when the azimuthal shape of the galaxy deviates from a perfect ellipse, $t_{exp}$ is the exposure time of the image, and mag zpt is the zero point magnitude of the image. Since \textsc{Galfit} also outputs the S\'ersic n values, we can also plot the one dimensional light profiles for each component. In \autoref{fig:pics} we plot five CCGs spanning the range of log(flux ratio) values along with their one dimensional S\'ersic light profiles. Since the fluxes are calculated using the two dimensional ellipsoidal shape of the galaxy, the one dimensional profile may not always match what we expect the log(flux ratio) value to be.

@@

We also note that there are some cases when \textsc{Galfit} cannot find a core or an envelope, and will instead fit an extremely large and faint component instead. When this happens (11 out of 96 cases), we classify this fit as either all core/all envelope depending on which component was bad, i.e., assigning log(flux ratio) = minimum of all flux ratios ($-0.93$) or maximum of all flux ratios ($+1.31$)\footnote{An example of this case is CCG rf0250, which is plotted on the far right of \autoref{fig:pics}.}. In six of 96 cases, \textsc{Galfit} fits identical \Reff\ values for both the first and second S\'ersic components. We inspect their S\'ersic plots by eye and see that these should be core-dominated CCGs. We assign these cases to have log(flux ratio) = maximum of all flux ratios ($+1.31$) as well.\footnote{An example of this case is CCG rf0003, which is plotted in the top right of \autoref{fig:imageplots}.}

@@

Galaxy groups are identified using the friends-of-friends algorithm of \citet{Berlind2006} with linking lengths modified as described in \citet{Eckert2016}, and the masses of the group halos are calculated based on the observed total $r$-band luminosity of galaxies in each group using abundance matching, as described in \citet{Blanton2007}. More information on group identification can be found in \citet{Eckert2016}. The nearest 2-dimensional neighbor distances are computed using the RA and Dec coordinates for each galaxy along with a requirement that the neighbor be within $\pm~500$~km~$^{-1}$ of the primary. Three-dimensional distances are also available based on Hubble's Law distances, however the added errors that come with peculiar velocities make these values less reliable.

@@

 \begin{figure*}[b]
\begin{center}
\includegraphics{faber-jackson_resolvesigmas.eps}
\caption{The Faber-Jackson relation (stellar mass vs. velocity dispersion) for the RESOLVE sample, CCGs, and the CSSs of the AIMSS catalog. We look for CCGs offset to higher $\sigma$ for its stellar mass, which may indicate tidal stripping as a possible formation scenario. The green point is M32, the prototypical cE, that is believed to be tidally stripped \citep{Faber1973}. In orange is the free floating cE discovered in \citet{Huxor2013} that is thought to be dissipatively formed.}
\label{fig:sigma}
\end{center}
\end{figure*}

@@

CCG rf0003 is core-dominated, lives intermediate between the blue and red sequences and has a low FSMGR ($\sim~0.10$). It resides in a low mass group (halo mass $\sim10^{10.9}$~\Msun) and is $>2$~Mpc from another galaxy, which we classify as free floating. Its $\sigma$ places it firmly along the main Faber-Jackson relation. All together, these clues point to a dissipatively-formed CCG. However, being near the green valley may indicate that this formation occurred relatively recently.

Lastly, rf0328 is also core-dominated and lives intermediate between the blue and red sequences, but has a higher FSMGR at $\sim0.6$, indicating considerable star formation taking place in the last Gyr. The galaxy resides in a low mass group and is $\sim0.4$~Mpc from a neighbor. Its $\sigma$ places it among the dissipatively formed CCGs, and like rf0003, its color and FSMGR may indicate this formation happened recently.

@@

\subsection{Crossover CCGs}
We classify rs0567, rs1186, rf0078, rf0492 as crossover CCGs, based on their small one component \Reff\ measurements ($\sim~500--700$~pc) and $\sigma$ values following the dissipative formation track. The CCGs rs0567, rs1186, and rf0078 are all three are mildly core-dominated galaxies. They live on the red sequence and display little star formation (FSMGR $> 0.1$) for all. CCGs rs1186 and rf0078 both have close neighbors ($\sim~0.2$~Mpc distance), but rs0567 has a nearest neighbor $\sim~0.7$~Mpc, which makes it quite similar to the free floating cE discovered by \citet{Huxor2013} (which also has a core-dominated light profile).

CCG rf0492 lies closest to the free floating cE from \citet{Huxor2013} in both \autoref{fig:sigma} and the top left of \autoref{fig:image plots}, but they don't share many other similarities. This CCG has a core+envelope profile and lives in an intermediate-sized group with halo mass~$\sim~10^{12}$~\Msun and neighbor within $\sim~0.11$~Mpc.

There are some CSSs in AIMSS with extremely small \Reff\ and low $\sigma$ (the dark squares at M$_{\star}~\sim~10^{8.5}$~\Msun\ and $\sigma~\sim~20~\text{km~s}^{-2}$), making them dE-like as well. We postulate that galaxies like these and the other crossover CCGs discussed above may also be the low-$z$ analogues to the ``red/blue nugget'' galaxies that are common at high-redshift with \Reff~$\sim~1$~kpc. \citet{Dekel2013} propose that at high redshifts, blue nuggets form when gaseous disks contract during dissipative processes (such as gas inflows to the central region of the disk) and then later quench to become red nuggets that are so common in the early Universe.

There are also two AIMSS objects with the opposite conditions: large \Reff\ and high $\sigma$ (the two dark triangles in \autoref{fig:sigma} with M$_{\star}~\sim~10^{8.5}$~\Msun\ and $\sigma~\sim~40-50~\text{km~s}^{-2}$). These dEs may be in the process of tidal stripping currently, and will move to the CSS-like track when the stripping is complete.

\begin{figure*}[b]
\begin{center}
\includegraphics[scale=0.7]{miniplots.eps}
\caption{\textbf{(Top left.)} deconvolved \Reff\ vs. stellar mass, \textbf{(Top right.)} the nearest two-dimensional neighbor vs. group halo mass, \textbf{(Bottom left.)} $u-r$ color vs. stellar mass, and \textbf{(Bottom right.)} FSMGR vs. baryonic mass for all galaxies in RESOLVE, the cEs and dEs of AIMSS, and the eight CCGs that have velocity dispersion information. This information, combined with \autoref{fig:sigma}, help us distinguish between formation scenarios for the CCG sample.}
\label{fig:miniplots}
\end{center}
\end{figure*}

\begin{figure*}[b]
\begin{center}
\includegraphics[scale=0.7]{imageplots.eps}
\caption{We show here \textbf{(a.)} deconvolved \Reff\ vs. stellar mass, \textbf{(b.)} the nearest two-dimensional neighbor vs. group halo mass, \textbf{(c.)} $u-r$ color vs. stellar mass, and \textbf{(d.)} FSMGR vs. baryonic mass for all galaxies in RESOLVE, the cEs and dEs of AIMSS, and the eight CCGs that have velocity dispersion information. This information, combined with \autoref{fig:sigma}, help us distinguish between formation scenarios for the CCG sample. We also note that rf0003 is one of the six cases where \textsc{Galfit} finds identical \Reff\ values for both the first and second S\'ersic components, and have hence set log(flux ratio) = maximum of all flux ratios ($+1.31$).}
\label{fig:imageplots}
\end{center}
\end{figure*}

>>>>

CSSs have half-light radii (\Reff) ranging typically from $\sim$10--600 pc \citep[e.g.,][]{Norris2014}, and there are multiple ideas for how they form. The smaller of the CSSs, UCDs may simply be the high mass extension of the GC population \citep{Drinkwater2000, Mieske2002}. The is also evidence that UCDs are created via the tidal stripping of nucleated dwarf galaxies \citep{Bekki2001, Bekki2003, Norris2011, Jennings2015, Zhang2015}. \citet{Seth2014} find a supermassive black hole at the center of another UCD, providing further evidence of tidal stripping being common for UCDs. Similarly, cEs are thought to be the result of tidal stripping events, as argued for the prototypical cE, M32 \citep{Choi2002, Graham2002, Huxor2011}. More evidence is provided by the discovery of tidal streams near cEs \citep{SmithCastelli2008a,Chilingarian2009} and one cE, studied in \citet{Kormendy1997}, that is believed to host a central massive black hole. On the other hand, \citet{Wirth1984}, \citet{Kormendy2009}, and \citet{Kormendy2012a} argue that cEs are the low mass extension to the normal E population created via dissipative formation in gas rich environments, such as during mergers or in the two-phase formation process detailed in \citet{Oser2010}. One of the most successful recent searches for CSSs is the AIMSS catalog \citep{Norris2014}: with many newly discovered UCDs and cEs to examine, the authors argue that all of the above scenarios for UCD and cE formation occur.

In contrast to CSSs, dwarf elliptical galaxies \citep[dEs;][]{Sandage1985} and their nucleated counterparts \citep[dE,Ns;][]{Binggeli1984} are quite common, especially in clusters where they were first discovered. In fact, \citet{Binggeli1991} find that of 225 galaxies present in the center of Virgo cluster, 174 are classified as dEs or dE,Ns based on their surface brightness profiles. While dEs are typically larger than CSSs with \Reff\ ranging from $\sim600$~pc up to $\sim2000$~pc \citep[e.g.,][]{Norris2014}, the cores of dE,Ns can reach down to CSS-like sizes and reside within larger envelopes that are dE-sized. Similar to cEs, dEs are often thought to be either tidally stripped remnants \citep{Crnojevic2014} or the low mass extension to elliptical galaxies \citep{Kormendy2012a}. They could also be the remnants of late-type disk galaxies or luminous blue compact dwarfs that have been ram-pressure stripped and quenched as they enter the cluster environment \citep{Lisker2013, Crawford2016a}. There is also evidence that dE,Ns become UCDs as they fall deeper into the cluster core and are further stripped \citep{Pfeffer2013,Zhang2015,Liu2015}.

Given the similarities in formation scenarios between CSSs and dEs, we introduce the term ``compact core galaxy'' or ``CCG'' to encompass CSSs and dEs with core \Reff\ up to 800~pc. The goal of this paper is to study these galaxies as part of a continuum of compact galaxies in order to differentiate between formation scenarios. Clues to how CCGs form may be given by their environments,  morphology i.e., one- or two-component structure, star formation histories, and kinematics. We highlight these data below.

%environments
\textit{Environments.} CSSs have been found in a large range of environments thus far. UCDs were first discovered in the Fornax cluster \citep{Hilker1999, Drinkwater2000} and have since been found in the cores of several other clusters \citep{Price2009,Madrid2010,Jones2006,Mieske2009,Misgeld2008}, in groups \citep{Evstigneeva2007}, and near field galaxies \citep{Hau2009,Norris2011}. M32 was first discovered in our Local Group \citep{Faber1973} near M31, and more cEs have later been found in clusters \citep{Chilingarian2007,SmithCastelli2012,Price2009} and other groups \citep{Huxor2011,Chilingarian2010}. As stated previously, dEs and dE,Ns are common in clusters \citep{SmithCastelli2012,Koo1994,Guzman1996,Crawford2016a}, but have also been found near groups \citep{Crnojevic2014,Penny2014}. Only cEs have been found ``free floating'', meaning there is no host galaxy at all: \citet{Huxor2013} and \citet{Paudel2014} both find one cE separated from other galaxies by $\sim~840$ and $\sim~600$~kpc, respectively.

@@

%structure
\textit{Morphologies.} CSSs have been found to exhibit either one component (i.e., just a core) or two component (i.e., a core plus a surrounding envelope of gas and stars) morphology. \citet{Graham2002} have shown that M32's light profile is best fit with a core plus a surrounding exponential disk profile, which they argue points toward a tidal-stripping origin. \citet{Pfeffer2013} use N-body simulations to predict that UCDs that are tidally stripped remnants will also display multi-component surface brightness profiles due to lingering outer galaxy structures. Conversely, dissipative processes such as the two-phase formation scenario proposed by \citet{Oser2010} cause cores to form as gas rushes to the center during mergers or the convergence of streams of cold gas and star formation begins. This core is then ``puffed up'' through time as it interacts with other galaxies. The free-floating cE discovered in \citet{Huxor2013}, shown to have only a one-component light profile, may be an example of the first step in this two-phase formation. It's important to note that these effects may vary based on the degree of stripping and how much time has passed since the stripping or dissipative formation occurred.

@@

For dEs and dE,Ns, there is similar diversity in colors. \citet{SmithCastelli2012} find dEs in the Antlia cluster with both red and blue colors. \citet{Drinkwater2000} and \citet{Ferrarese2006} study the colors of dE,Ns and find that the cores of dE,Ns tend to have younger stellar populations compared to their host galaxies. \cite{Grant2005} also find that two-fifths of the Virgo dE,Ns have young cores compared to their envelopes, while three-fifths display the opposite trend.

@@

  We use the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog \citep{Norris2014,Forbes2014,Janz2015} as a reference sample for our CCGs.  AIMSS is a catalog of spectroscopically confirmed CSSs found near field galaxies and in groups and clusters, and includes both previously known and newly discovered objects. The AIMSS CSS discovery process was as follows. First, a search was conducted in the HyperLeda redshift catalog \citep{Paturel2003} for all galaxies with M$_{\rm B}~<~-15$ and distances between $\sim 7$ and 200 Mpc (close enough to ensure any CSSs with \Reff\ $> 50$ pc would be resolved in any available HST imaging). The team then searched the Hubble Space Telescope archive for WFCP2, ACS, and WFC3 imaging within 150 kpc in projection of the selected galaxies. Next, Source Extractor was run on the HST images, and candidates were identified using a training set of previously known CSSs from the literature. After vetting by eye and cross-matching to ensure none are previously known, spectra were obtained for redshift confirmation and measurements of velocity dispersions. AIMSS also includes literature data for previously known UCDs, cEs, dEs, dE,Ns, dwarf spheroidals, dwarf S0s, young massive clusters, and Es. The catalog provides a compilation of absolute $V$-band magnitude, stellar mass, half-light radius, and velocity dispersion for each of its objects. Thus, though not a statistically-defined sample, AIMSS provides a useful reference catalog to which we can compare our CCGs. We also note that the objects in AIMSS are not decomposed, meaning their \Reff\ are all single component fits. We discuss this more in \autoref{discussion}.

@@

\textsc{Galfit} needs the following input files to function properly: an initial input file, an image of the galaxy, a PSF image, an image mask, and a constraint file. We obtain or construct these items as follows:

@@

\item[The initial input file]{The initial input file gives \textsc{Galfit} the file paths to the image, PSF, mask, and constraint file, and also holds the initial guesses for our fit parameters. For the one component fits, we set up our input file to include a section to measure the level of the sky background and another section to fit a S\'ersic profile \citep{Sersic1963, Sersic1968} to the galaxy. The S\'ersic model will find a best fit for the following parameters: central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle. These initial values for these parameters can just be rough guesses, but for our purposes, we use values for the magnitude, \Reff, b/a, and PA that are derived from RESOLVE's custom processed photometric data (see \autoref{phot} for more details).}

@@

where $\Sigma_e$ is the surface brightness at \Reff, $R(C_0; m)$ is a geometric correction factor when the azimuthal shape of the galaxy deviates from a perfect ellipse, $t_{exp}$ is the exposure time of the image, and mag zpt is the zero point magnitude of the image. Therefore the integrated magnitudes calculated take into account the two dimensional shape of the galaxy being fit. Since \textsc{Galfit} also outputs the S\'ersic n values, we can also plot the one dimensional light profiles for each component. In \autoref{fig:pics} we plot five CCGs spanning the range of log(flux ratio) values along with their one dimensional S\'ersic light profiles. Since the fluxes are calculated using the two dimensional ellipsoidal shape of the galaxy, the one dimensional profile may not always match what we expect the log(flux ratio) value to be.

@@

We also note that there are some cases when \textsc{Galfit} cannot find a core or an envelope, and will instead fit an extremely large and faint component instead. When this happens (11 out of 96 cases), we classify this fit as either all core/all envelope depending on which component was bad, i.e., assigning log(flux ratio) = minimum of all flux ratios ($-0.93$) or maximum of all flux ratios ($+1.31$)\footnote{An example of this case is CCG rf0250, which is plotted on the far right of \autoref{fig:pics}.}. In six of 96 cases, \textsc{Galfit} fits identical \Reff\ values for both the first and second S\'ersic components. We inspect their S\'ersic plots by eye and see that these should be core-dominated CCGs. We assign these cases to have log(flux ratio) = maximum of all flux ratios ($+1.31$) as well\footnote{An example of this case is CCG rf0003, which is plotted in the top right of \autoref{fig:imageplots}.}.

@@

Galaxy groups are identified using the friends-of-friends algorithm of \citet{Berlind2006} with linking lengths modified as described in \citet{Eckert2016}, and the masses of the group halos are calculated based on the observed total $r$-band luminosity of galaxies in each group using abundance matching, as described in \citet{Blanton2007}. More information on group identification can be found in \citet{Eckert2016}. The nearest two-dimensional neighbor distances are computed using the RA and Dec coordinates for each galaxy along with a requirement that the neighbor be within $\pm~500$~km~$^{-1}$ of the primary. Three-dimensional distances are also available based on Hubble's Law distances, however the added errors that come with peculiar velocities make these values less reliable.

@@

 \begin{figure*}[b]
\begin{center}
\includegraphics{faber-jackson_resolvesigmas.eps}
\caption{The Faber-Jackson relation (stellar mass vs. velocity dispersion) for the RESOLVE sample, CCGs, and the cEs and dEs of the AIMSS catalog. We look for CCGs offset to higher $\sigma$ for its stellar mass, which may indicate tidal stripping as a possible formation scenario. The green point is M32, the prototypical cE, that is believed to be tidally stripped \citep{Faber1973}. In orange is the free floating cE discovered in \citet{Huxor2013} that is thought to be dissipatively formed.}
\label{fig:sigma}
\end{center}
\end{figure*}

@@

CCG rf0003 is core-dominated, lives intermediate between the blue and red sequences and has a low FSMGR ($\sim~0.10$). It resides in a low mass group (halo mass $\sim10^{10.9}$~\Msun) and is $>2$~Mpc from another galaxy, which we classify as free floating. Its $\sigma$ places it firmly along the main Faber-Jackson relation. All together, these clues point to a dissipatively-formed CCG, perhaps through the convergence of cold streams. Residing near the green valley indicate that this formation may have occurred relatively recently.

Lastly, rf0328 is also core-dominated and lives intermediate between the blue and red sequences, but has a higher FSMGR at $\sim0.6$, indicating considerable star formation taking place in the last Gyr. The galaxy resides in a low mass group and is $\sim0.4$~Mpc from a neighbor. Its $\sigma$ places it among the dissipatively-formed CCGs, perhaps due to cold gas streams converging or even a merger, given its environment. Like rf0003, its color and FSMGR may indicate this formation happened recently.

@@

\subsection{Crossover CCGs}
We classify rs0567, rs1186, rf0078, rf0492 as crossover CCGs, based on their small one component \Reff\ measurements ($\sim~500-700$~pc) and $\sigma$ values following the dissipative formation track. The CCGs rs0567, rs1186, and rf0078 are all three are mildly core-dominated galaxies. They live on the red sequence and display little star formation (FSMGR $> 0.1$) for all. CCGs rs1186 and rf0078 both have close neighbors ($\sim~0.2$~Mpc distance), but rs0567 has a nearest neighbor $\sim~0.7$~Mpc, which makes it quite similar to the free floating cE discovered by \citet{Huxor2013} (which also has a core-dominated light profile).

CCG rf0492 lies closest to the free floating cE from \citet{Huxor2013} in both \autoref{fig:sigma} and the top left of \autoref{fig:imageplots}, but they don't share many other similarities. This CCG has a core+envelope profile and lives in an intermediate-sized group with halo mass~$\sim~10^{12}$~\Msun and neighbor within $\sim~0.11$~Mpc. It lives on the red sequence and has low FSMGR ($<~0.1$), making it a good candidate of a CCG formed via ram pressure stripping as a dwarf (perhaps an LCBD) fell into the group halo.

We note that there are two cEs in AIMSS with extremely small \Reff\ and low $\sigma$ (the dark squares at M$_{\star}~\sim~10^{8.5}$~\Msun\ and $\sigma~\sim~20~\text{km~s}^{-2}$ in \autoref{fig:sigma}), and we classify these as crossovers as well. We postulate that galaxies like these and the other crossover CCGs discussed above may be the low-$z$ analogues to the ``red/blue nugget'' galaxies that are common at high-redshift with \Reff~$<~1$~kpc. \citet{Dekel2013} propose that at high redshifts, blue nuggets form when gaseous disks contract during dissipative processes (such as gas inflows to the central region of the disk) and then later quench to become red nuggets that are so common in the early Universe.

There are also two AIMSS objects with the opposite conditions: large \Reff\ and high $\sigma$ (the two dark triangles in \autoref{fig:sigma} with M$_{\star}~\sim~10^{8.5}$~\Msun\ and $\sigma~\sim~40-50~\text{km~s}^{-2}$). These dEs may be in the process of tidal stripping currently and may move to the CSS-like track when the stripping is complete.

\begin{figure*}[b]
\begin{center}
\includegraphics[scale=0.7]{miniplots.eps}
\caption{\textbf{(Top left.)} single-component deconvolved \Reff\ vs. stellar mass, \textbf{(Top right.)} the nearest two-dimensional neighbor vs. group halo mass, \textbf{(Bottom left.)} $u-r$ color vs. stellar mass, and \textbf{(Bottom right.)} FSMGR vs. baryonic mass for all galaxies in RESOLVE, the cEs and dEs of AIMSS, and the eight CCGs that have velocity dispersion information. We emphasize that the \Reff\ values plotted in the top left panel are not the two-component core \Reff\ values as in \autoref{fig:radius} in order to compare our radius measurements with the CSSs of AIMSS that have not been decomposed.}
\label{fig:miniplots}
\end{center}
\end{figure*}

\begin{figure*}[b]
\begin{center}
\includegraphics[scale=0.7]{imageplots.eps}
\caption{The light profiles for the eight CCGs with velocity dipersion measurements. The $rgb$ images are from the SDSS-DR8 image list tool. Above each plot is the value of the logarithm of the ratio of the core and envelope fluxes, which are given via the symbol colors in \autoref{fig:sigma} and \autoref{fig:miniplots}. We also note that rf0003 is one of the six cases where \textsc{Galfit} finds identical \Reff\ values for both the first and second S\'ersic components, and have hence set log(flux ratio) = maximum of all flux ratios ($+1.31$).}
\label{fig:imageplots}
\end{center}
\end{figure*}
